Simply Grasping Simple Shapes:\\ Commanding a Humanoid Hand with a Shape-Based Synergy

### 2017-10-29 draft_springer_2.tex
Section 5.1 updated

The SynGrasp model provided a useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed. Going forward, SynGrasp is useful for other synergy types such as pinch grasp which has contact forces only in the fingers and does not require use of the palm.

@@

The SynGrasp model assumes the friction among multiple joints actuated with a single tendon is equal, allowing all of the joints to move in unison. However, in practice this is not the case. On the R2 hand, especially on the ring and little fingers, the first joint will move exclusively until it comes into contact with the object, then the next joints will begin to actuate. This resulted in poor finger placement for the ring and little fingers on initial model validation and the closing values had to be increased to obtain a firm grip using those fingers. The result of this can be seen in Fig. \ref{pinkymodels}

>>>>

The SynGrasp model provided a useful method to determine a starting point for grasp refinement, however, the SynGrasp model remains an idealized model of the robot hand. Many aspects could not be accurately modelled and had to be adjusted through the model validation process, as discussed below. Future additions to the software to allow more realistic actuation could include friction models and more control over the geometry of the hand, as R2's palm is larger than the model allowed.

@@

The SynGrasp model assumes the friction among multiple joints actuated with a single tendon is equal, allowing all of the joints to move in unison. However, in practice this is not the case. On the R2 hand, especially on the ring and little fingers, the first joint will move exclusively until it comes into contact with the object, then the next joints will begin to actuate. This resulted in poor finger placement for the ring and little fingers on initial model validation and the closing values had to be increased to obtain a firm grip using those fingers (see Fig \ref{pinkymodels}).
